Applying Deep Learning to Acoustic Analysis in the PICO-60 Dark Matter Detector

### 2018-08-07 documentation/paper.tex
Added class-wise standard deviation information for supervised learning

Once the audio was cropped properly, $DeepConv(\omega)$ achieved a maximum of 77\% accuracy on validation data. Using the same network architecture (except for the input layer), $DeepConvWithPos(\omega, \chi)$ achieved 85\%. The maximum obtained on a grid search with position correction was 91\%. While this is not a drastic improvement, it is a fairly strong indication that the network is able to extract meaningful information from the position, which may be used in an internal position correction of the volume.

@@

It became evident very quickly that, without $WallCut(D)$ a high resolution was not required to get a high accuracy relative to the ground truth data. $FourierMLP(\beta_{8})$ managed an excellent 98\% validation accuracy by this metric. Increasing the number of bands, even up to $FourierMLPWithPos(beta_{20}, \chi)$, did not improve the results; accuracy only reached 94\%.

@@

The higher resolution demonstrated significant power when $WallCut(D)$ was not applied, and only \\ $QualCut(MultiCut(D))$ was used. $FourierMLPWithPos(\beta_{20}, \chi)$ achieved only 92\% accuracy (2 percentage points lower than the same configuration without $WallCut(D)$). $FourierMLPWithPos(\beta_{40}, \chi)$ also managed 92\% validation accuracy. However, training on $\beta_{50,001}$, which does not incorporate any banding, improved this figure to a maximum of 97\%.

@@

$WallCut(D)$ was not applied to the training set, because while the resonance in the vessel varies greatly depending on the position of the bubble, any visual differences in the bubble should not. In addition, applying it reduces the size of the training set considerably.

@@

Throughout a variety of different network architectures, the best validation accuracy obtained was 85\%. (The corresponding training accuracy of 100\% indicates that severe overfitting is taking place.) It is likely fitting on some form of noise within $\iota$, since the network's predictions seem almost random when represented graphically (as seen in Figure \ref{image_window}). The fact that throughout many trials (including a grid search), no good performance on validation data was observed, provides significant evidence that images provide insufficient information for effective discrimination.

>>>>

Once the audio was cropped properly, $DeepConv(\omega)$ achieved a maximum of 77\% accuracy on validation data. Using the same network architecture (except for the input layer), $DeepConvWithPos(\omega, \chi)$ achieved 85\%. The maximum obtained on a grid search with position input was 91\% (although with a high class-wise standard deviation of 0.61). While this is not a drastic improvement, it is a fairly strong indication that the network is able to extract meaningful information from the position, which may be used in an internal position correction of the volume.

@@

It became evident very quickly that, without $WallCut(D)$, a high resolution was not required to get a high accuracy relative to the ground truth data. $FourierMLP(\beta_{8})$ managed an excellent 98\% validation accuracy, and also produced a mean class-wise standard deviation of 0.29. Increasing the number of bands, even up to $FourierMLPWithPos(beta_{20}, \chi)$, did not improve the results; accuracy only reached 95\%, with an increased mean standard deviation of 0.42.

@@

The higher resolution demonstrated significant power when $WallCut(D)$ was not applied, and only \\ $QualCut(MultiCut(D))$ was used. $FourierMLPWithPos(\beta_{20}, \chi)$ achieved only 92\% accuracy (2 percentage points lower than the same configuration without $WallCut(D)$). $FourierMLPWithPos(\beta_{40}, \chi)$ also managed 92\% validation accuracy. However, training on $\beta_{50,001}$, which does not incorporate any banding, improved this figure to a maximum of 97\%. However, that epoch had a relatively high standard deviation, at 0.47.

@@

@@

Throughout a variety of different network architectures, the best validation accuracy obtained was 85\%. The corresponding training accuracy of 100\% indicates that severe overfitting is taking place. Also, the class-wise standard deviation was a very high 0.95, which implies its decisions are nearly random (as is apparent in \ref{image_window}). It is likely fitting on some form of noise within $\iota$. The fact that throughout many trials (including a grid search), no good performance on validation data was observed, provides significant evidence that images provide insufficient information for effective discrimination.
